cardinalR: Generating interesting high-dimensional data structures

### 2025-05-04 paper-cardinalR.Rmd
Added updated description for Swiss roll

To generalize the Swiss roll structure to arbitrary dimensions, we introduce a function `gen_swissroll(n, p, w)`, which constructs a high-dimensional version of the classic 3D Swiss roll while preserving its core characteristics.

The function generates `n` points in a `p`-dimensional space, where the first two dimensions (`X_1, X_2`) define the primary Swiss roll shape using a parametric equation:

$$
X_1 = t \cos(t), \quad X_2 = t \sin(t), \quad \text{where } t \sim U(0, 3\pi)
$$

The third dimension (`X_3`) introduces variation perpendicular to the roll, sampled uniformly from \([-1,1]\). Additional dimensions (`X_4` to `X_p`) extend the data structure by applying a **sinusoidal transformation** of the parameter `t`, ensuring continuity in higher-dimensional spaces:

$$
X_i = \frac{\sin(i t)}{i}, \quad \text{for } i \geq 4.
$$

This transformation ensures a gradual decay in variance across dimensions, mimicking real-world high-dimensional structures where later dimensions often capture subtler variations.

>>>>

To further generalize the Swiss roll structure and introduce realistic noise, we define a function `gen_swissroll(n, p, w)`, where `n` is the number of points, `p` is the total number of dimensions, and `w` is the vertical range in the third dimension.

The first three dimensions form the classic $3\text{-}D$ Swiss roll shape:

$$
X_1 = t \cos(t), \quad X_2 = t \sin(t), \quad X_3 \sim U(w_1, w_2), \quad \text{with } t \sim U(0, 3\pi)
$$

For $p > 3$, the remaining $p - 3$ dimensions are filled with small Gaussian noise to simulate high-dimensional complexity.
